\hypertarget{crossplatformexport_8h}{
\subsection{crossplatformexport.h File Reference}
\label{crossplatformexport_8h}\index{crossplatformexport.h@{crossplatformexport.h}}
}


This file is used on some platforms to determine what data should be read and written to and from a shared/dynamic library.  




\subsubsection{Detailed Description}
This file is used on some platforms to determine what data should be read and written to and from a shared/dynamic library. Currently this file uses \_\-\_\-declspec(dllexport) and \_\-\_\-declspec(dllimport) on the windows platform to control what is imported from or exported to the \hyperlink{namespaceMezzanine}{Mezzanine} DLL. If WINDOWS if defined then MEZZ\_\-LIB will be set to either \char`\"{}\_\-\_\-declspec(dllexport)\char`\"{} or \char`\"{}\_\-\_\-declspec(dllimport)\char`\"{}. Every Class, template, function variable, and other item intended to be in \hyperlink{namespaceMezzanine}{Mezzanine} is tagged with MEZZ\_\-LIB. \par
 \par


During compilation of the \hyperlink{namespaceMezzanine}{Mezzanine} engine \_\-\_\-declspec(dllexport) tells the compiler that a given item (a function, class, template, etc...), should be included in the dll and made available for use in games (or whatever kind of applicaitons use \hyperlink{namespaceMezzanine}{Mezzanine}). This header sets MEZZ\_\-LIB to \_\-\_\-declspec(dllexport) if EXPORTINGPHYSGAMEDLL is set. If \hyperlink{namespaceMezzanine}{Mezzanine} is compiled using the cmake build provided then this is handle automatically. If the cmake build is not used, then this file will attempt to detect if the platform it is running on is windows or not. It is preferable that you configure your build environment to define WINDOWS and EXPORTINGMEZZANINEDLL if you are compiling this on windows without the provided cmake build. \par
 \par


Compilation of applications using \hyperlink{namespaceMezzanine}{Mezzanine} \_\-\_\-declspec(dllimport), tells the compiler what to expect from the dll and may make optimizations available with some compilers. This is automatically set if you use the cmake build, if you aren't this file will attempt to determine if you are running windows. It is best to set the build envirnoment of your game or applciation to define WINDOWS, if possible copy of our cmake builds for Catch! or the EngineDemo. \par
 \par


The Macro MEZZ\_\-LIB is declared as empty if WINDOWS is not defined, as should be the case if LINUX or MACOSX is defined. \par
 \par
 

Definition in file \hyperlink{crossplatformexport_8h_source}{crossplatformexport.h}.

